A Survey of Range-Only SLAM Techniques and Sensors

### 2018-11-09 Paper.tex
Added reference to SEIF section
Added paper Robot-Beacon Distributed Range-Only SLAM for Resource-Constrained Operation to the SEIF section and .bib

Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented. An information filter (IF) algorithm is mentioned in\cite{Torres-Gonzalez2014}. In EKF the Gaussians are represented in the form of their moments, mean and variance, whereas in a information filter the Gaussians are in their conical parameterization which comprises of an information matrix and information vector. 
%Hence what is computationally complex in EKF is simple in the other and vice versa. Hence they are dual to each other.
Sparse Extended information filters are derived from the  information filter but it maintains a sparse representation of the information matrix. This makes the SEIF more scalable and efficient as show in \cite{Torres-Gonzalez2014}.

The information filter stores the relation between any two state elements in the information matrix also known as links. The higher the value of the link the stronger is the relationship between the two state variables and the more it is gonna effect the robots state. SEIF maintains a sparse information matrix by eliminating weak inks that are below a certain threshold thus reducing the computational complexity involved.

In \cite{Torres-Gonzalez2014} the computational complexity is reduced by utilizing the computational capabilities of the nodes or radio  beacons. Here the robot computes the prediction stage of the iteration, sends the information to the beacons where the update process is completed. Hence the computation burden on the robot is reduced. In addition, inter-beacon measurements are factored in to reduce uncertainty even further. In \cite{Torres-Gonzalez2017} the SEIF method is evaluated and compared for 3d SLAM using an octorotor In conclusion this method had better estimates and lesser computational burden than the traditional RO SLAM method using EKF.

>>>>

Information filters work on the same underlying Gaussian belief principle as that of EKF but vary in the way that Gaussian beliefs are represented. An information filter (IF) algorithm is mentioned in\cite{Torres-Gonzalez2014}. In EKF the Gaussians are represented in the form of their moments, mean and variance, whereas in a information filter the Gaussians are in their conical parameterization which comprises of an information matrix and information vector. 
%Hence what is computationally complex in EKF is simple in the other and vice versa. Hence they are dual to each other.
Sparse Extended information filters are derived from the  information filter but it maintains a sparse representation of the information matrix. This makes the SEIF more scalable and efficient as show in \cite{Torres-Gonzalez2014}.

%Jeez, this explains the information filter in suuuuch abstract terms
The information filter stores the relation between any two state elements in the information matrix also known as links. The higher the value of a link, the stronger the relationship between two state variables which in turn affects the robots state. SEIF maintains a sparse information matrix by eliminating weak links that are below a certain threshold thus reducing the computational complexity involved.

In \cite{Torres-Gonzalez2014} the computational complexity is reduced by utilizing the computational capabilities of the nodes or radio  beacons. Here the robot computes the prediction stage of the iteration, sends the information to the beacons where the update process is completed. Hence the computation burden on the robot is reduced. In addition, inter-beacon measurements are factored in to reduce uncertainty even further. In \cite{Torres-Gonzalez2017} the SEIF method is evaluated and compared for 3d SLAM using an octorotor In conclusion this method had better estimates and lesser computational burden than the traditional RO SLAM method using EKF. \cite{Torres-Gonzalez2017a} extends this method by integrating a distributed information-driven measurement allocation tool with the SEIF to allow for dynamic selection of measurements. The end goal being to create a scheme that utilizes robot-beacon and inter-beacon measurements to increase accuracy while maintaining resource-consumption efficiency and scalability. Thus, creating a scalable distributed RO-SLAM scheme with a focus towards resource limited operations.
